Verifying Demonstrations

### 2017-07-24 RelatedWork.tex
Changes refkey for CrowdCount
Adds CrowdSize app to Related Work

@@

The most closely related work is \textcite{CrowdCount.org}.
This is a web service which lets Alice create an event and Bob can submit his 
location to register that he is in Alice's event.
This solves the problem that it counts everyone (who submitted), not just the 
count at the snapshot of the photos.
However, there is no verification, i.e.\ the service must be trusted, nor 
anything preventing Bob from submitting twice (eligibility verification).
Another downside is that the service also requires an Internet connection 
during the event to register as a participant.
This can make it difficult to use if e.g.\ Alice has organized a protest 
against the government, who shuts down the cellular network or Internet 
backbone as a means to censor the protest.

\begin{frame}<presentation>
  \begin{solution}[CrowdCount\footfullcite{CrowdCount.org}]
    \begin{itemize}
      \item Register an upcoming event.
      \item Let people \enquote{check-in} by submitting their location.
    \end{itemize}
  \end{solution}

>>>>

There is an app CrowdSize~\cite{CrowdSize} which estimates the size of a crowd 
based on a selected space.
Then the user selects one of three pre-set density estimates: light, medium or 
dense.
This is similar to the method usually used by police, e.g.\ for the protests in
Seoul
\blockcquote{2016DemonstrationsInSeoul}{%
  \textins*{p}olice presume\textins*{d} that, when sitting, six people would 
  fill a space of 
  3.3 square meters
  \textelp{}
  The same area would hold nine or 10 people when standing%
}.

@@

The most closely related work is \textcite{CrowdCount}.
This is a web service which lets Alice create an event and Bob can submit his 
location to register that he is in Alice's event.
This solves the problem that it counts everyone (who submitted), not just the 
count at the snapshot of the photos.
However, there is no verification, i.e.\ the service must be trusted, nor 
anything preventing Bob from submitting twice (eligibility verification).
Another downside is that the service also requires an Internet connection 
during the event to register as a participant.
This can make it difficult to use if e.g.\ Alice has organized a protest 
against the government, who shuts down the cellular network or Internet 
backbone as a means to censor the protest.

\begin{frame}<presentation>
  \begin{solution}[CrowdCount\footfullcite{CrowdCount}]
    \begin{itemize}
      \item Register an upcoming event.
      \item Let people \enquote{check-in} by submitting their location.
    \end{itemize}
  \end{solution}
